Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: opening paragraph to methods sec

BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
related to the asymptotic $r^{-1}$ fall-off of the scalar field.
%
This charge is not an independent parameter, and depends on the BH's mass and spin, %~\cite{Berti:2018cxi},
thus being a ``secondary hair''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
%
Since the scalar field is coupled to a curvature scalar, the $Q$ is larger (smaller)
the smaller (larger) the BH's mass is.

@@

BHs in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
and in Refs.~\cite{Cardoso:2018ptl} in the dimension-eight EFT.
%
In general

@@

@@

We start by reviewing the parametrized ringdown spin expansion coefficients (ParSpec)
framework introduced in Ref.~\cite{Maselli:2019mjd}, but following
some of the notation used in Ref.~\cite{Carullo:2021dui}.

>>>>

BHs in EdGB gravity have scalar hair, to which we can associate a (monopole) scalar charge $Q$,
related to the asymptotic $r^{-1}$ fall-off of the scalar field.
%
This charge is not an independent parameter, and depends on the BH's mass and spin, %~\cite{Berti:2018cxi},
thus being a ``secondary hair''~\cite{Coleman:1991ku,Herdeiro:2015waa}.
%
Since the scalar field is coupled to a curvature scalar, $Q$ is larger (smaller)
the smaller (larger) the BH's mass is.

@@

In general \dots
%
\hs{Describe PN works.}

The QNMs of nonrotating BHs where calculated in in Refs.~\cite{deRham:2020ejn,Cano:2020cao} in the dimension-six EFT
and in Refs.~\cite{Cardoso:2018ptl,Cano:2020cao} in the dimension-eight EFT.
%
Ref.~\cite{Cano:2020cao} calculated the leading-order in BH spin corrections to the QNM spectra.

@@

Having reviewed the modified gravity theories we will consider, we now present
the frameworks upon which we will build our waveform model to confront these
theories against GW observations.
%
We will start by reviewing the theory-agnostic parametrized ringdown
spin-expansion coefficients (ParSpec) expansion in
Sec.~\ref{sec:review_parspec}.
%
Next, in Sec.~\ref{sec:review_pSEOB}, we will review our full
inspiral-(plunge)-merger-ringdown (IMR) BBH waveform model we
use~\cite{Brito:2018rfr,Ghosh:2021mrv} and explain how we include the ParSpec
expansion into it.
%
Finally, in Sec.~\ref{sec:theory_specific_qnm}, we show how we can map
theory-specific QNM calculations in modified gravity theories onto the
theory-agnostic free coefficients in the ParSpec expansion.
%
Ultimately, this provides with an IMR BBH waveform model, with the ringdown
informed with QNM calculations in specific beyond-GR theories.

@@

We start by reviewing the ParSpec
framework introduced in Ref.~\cite{Maselli:2019mjd}, but following
some of the notation used in Ref.~\cite{Carullo:2021dui}.
